---
title: "Reproducible Research"
author: "Kelly Schumann"
date: "6/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data...

This report was generated by the Activity Monitoring data requested in the Project specifications. The consists of 3 fields  * steps  * date  * interval (each interval is a 5 second timeslot with the first starting at 12:00AM). NA in the steps variable exists and will be replaced with 0. There are 17568 observations within the dataset, starting on Oct 1, 2012 12:00AM, thru Nov 30, 2012 11:55PM.

The 9 items to be committed
1. The git repo link and SHA-1  - [This repository](https://github.com/KellySchumann/Reproducible)

2. 
```{r}

```

## Plots include are stating the commitment requirements of the submission.

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
